Manuscript Figures for Genome Biology

### 2018-05-02 manuscript_figures/manuscript_figures.Rmd
Suggestion for Fig4

# reorder rows and columns
ranks_avg$casestudy <- factor(ranks_avg$casestudy, 
                              levels=unique(ranks_avg$casestudy[order(ranks_avg$nmethods)]))
ranks_avg$method <- factor(ranks_avg$method,
                           levels=unique(ranks_avg$method[order(ranks_avg$meta_rank)]))

@@

Fig4
ggsave(file.path(outdir, "Figure4.pdf"), width=6, height=4, dev = pdf)
```

>>>>

# reorder rows and columns
ranks_avg$casestudy <- factor(ranks_avg$casestudy, 
                              levels=unique(ranks_avg$casestudy[order(ranks_avg$nmethods)]))
ranks_avg$method <- factor(ranks_avg$method,
                           levels=rev(unique(ranks_avg$method[order(ranks_avg$meta_rank)])))

@@

Fig4
ggsave(file.path(outdir, "Figure4.pdf"), width=6, height=4, dev = pdf)

##
## AR: alternative suggestion to heatmap, feel free to discard! ##
##
ranks_avg$method <- factor(ranks_avg$method,
                           levels=rev(unique(ranks_avg$method[order(ranks_avg$meta_rank)])))
Fig4b <- ggplot( ranks_avg, aes(x=method, y=mean_rank, group=casestudy, col=casestudy) ) +
  geom_line() + geom_point() +
  labs(y="Mean rank", x="", col="Case study") +
  theme(axis.text.x=element_text(angle=25, vjust=1, hjust=1))
Fig4b
```
